---
title: "shapez"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/nliftman/SDS270PROJ2/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/nliftman/SDS270PROJ2/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Purpose

This package calculates the area and volume of simple, and somewhat complex shapes. It also includes a dataset with the first 1000 prime numbers. 

## Target Audience

There are two target audiences of our package. One is the user who wants R to run just like a calculator, so these functions are used to calculate these shapes. The other target audience is a young child first getting familiar with R, and writing code in R. They can use these functions to understand R and writing R code from the perspective of calculations they already understand!

## Installation

You can install the development version of shapez like so:

```{r, eval=FALSE}
remotes::install_github("nliftman/shapez")
```

## Examples 
### Area

Calculations of area of a circle with a graph: 

```{r example}
library(shapez)
area_circle(4, 1)
```

Calculations of area of a pentagon without a graph:
```{r}
area_pentagon(3, 4, 0)
```

Calculations of area of octagon with a graph:
```{r}
area_octagon(6, 1)
```

### Volume

Calculations of volume of sphere:
```{r}
library(shapez)
sphere(7, "volume")
```

Calculations of surface area of sphere:
```{r}
sphere(1982, "surface area")
```

Calculations of volume & surface area of sphere:
```{r}
sphere(4.999, 10, "both")
```
or
```{r}
sphere(4.999, 10)
```

### Dataset

Look at the first 10 prime numbers, and if they are even or odd!

```{r}
head(primes, 10)
```

