---
title: "shapez"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Purpose

This package calculates the area and volume of simple, and somewhat complex shapes. It also includes a dataset with the first 1000 prime numbers. 

## Target Audience

There are two target audiences of our package. One is the user who wants R to run just like a calculator, so these functions are used to calculate these shapes. The other target audience is a young child first getting familiar with R, and writing code in R. They can use these functions to understand R and writing R code from the perspective of calculations they already understand!

## Installation

You can install the development version of shapez like so:

```{r}
#remotes::install_github("nliftman/shapez")
```

## Examples Area

Calculations of area of a circle: 

```{r example}
library(shapez)
area_circle(4)
```

Calculations of area of a pentagon:
```{r}
area_pentagon(3, 4)
```

Calculations of area of octagon:
```{r}
area_octagon(6)
```

Calculations of volume of sphere:
```{r}
sphere_volume(7)
```

Calculations of volume of square pyramid:
```{r}
square_pyramid_volume(2, 2)
```

Calculations of volume of tetrahedron:
```{r}
tetrahedron_volume(1982)
```

## Package Proposal

We will continue working on this package to do calculations of volume and area; however, we will also start adding more complicated shapes and will be adding perimeter and surface area functions. Additionally, we hope to add functions that find other geometric properties relevant to an individual shape such as base area, diagonal lengths, circumferences, etc. The user would then have an option to display all the relevant properties values for their shape when they call the volume function on it. We also hope to build our functions better, possibly instead of using for loops using the map function. 

