---
title: "shapez package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shapez}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette summarizes the various information scattered throughout the R documentation and brings it together in one place. It goes through all of the functions in the package, their specifications, and examples.

### Loading the Package 

```{r setup}
library(shapez)
```

## Area Functions
### Area of a Rectangle

This function `area_square(width, height, graph)` calculates the area of a rectangle, along with, when requested a graph of the rectangle in question. 

The function requires `width`, `height`, and `graph` inputs, where `width` is the width of the rectangle, and `height` is the height. The final input `graph`, asks the user whether they would like the rectangle to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `width` and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_square(x,y)`, to do the graphing for it. All of the graphing function can be called on their own, but are less user friendly:
```{r}
graph_square(3,5)
```


This calculates the area of a rectangle with no graph.
```{r}
area_rectangle(3, 5, 0)
```

This calculates the area of a rectangle and includes a graph.
```{r}
area_rectangle(3, 5, 1)
```

### Area of a Circle

This function `area_circle(radius, graph)` calculates area of a circle, along with, when requested a graph of the circle in question. 
The function requires `radius`, and `graph` inputs, where `radius` is the radius of the circle. The other input `graph`, asks the user whether they would like the shape to be graphed. Imputing a 0 will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `radius` input, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_circle(x)`, to do the graphing for it.

This calculates the area of a circle with no graph.
```{r}
area_circle(3, 0)
```

This calculates the area of a circle and includes a graph.
```{r}
area_circle(3, 1)
```

### Area of a Triangle

This function `area_triangle(base, height, graph)` calculates the area of a triangle, along with, when requested a graph of the triangle in question. 

The function requires `base`, `height`, and `graph` inputs, where `base` is the base of the triangle, and `height` is the height. The final input `graph`, asks the user whether they would like the triangle to be graphed. Imputing a 0 will simply compute the area and not graph the shape; however, the user must know whether the triangle is a right or isosceles triangle to graph it. Inputting a 1 indicates that the triangle is an isosceles and inputting a 2 indicates it is a right triangle, and they will be graphed as such. 

Any negative or string inputs will throw an error for the `base` and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_triangle(x,y,type)`, to do the graphing for it.

This calculates the area of a triangle with no graph.
```{r}
area_triangle(3, 5, 0)
```

This calculates the area of an isosceles triangle with a graph.
```{r}
area_triangle(3, 5, 1)
```

This calculates the area of an right triangle with a graph.
```{r}
area_triangle(3, 5, 2)
```

### Area of a Trapezoid

This function `area_trapezoid(base_1, base_2, height, graph)` calculates the area of a $regular$ trapezoid along with, when requested, a graph of the trapezoid in question. 

The function requires `base_1`, `base_2`, `height`, and `graph` inputs, where `base_1` is the length of the bottom base, `base_2` is the length of the top base, and `height` being the height of the trapezoid. The final input `graph`, asks the user whether they would like the trapezoid to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `base_1`, `base_2`, and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. This function calls another function `graph_trapezoid(x,y,z)`, to do the graphing for it.

The main purpose of the graph is to help people visualize what area is being measuring. 

This calculates the area of a trapezoid with no graph.
```{r}
area_trapezoid(24, 2459, 4, 0)
```

This calculates the area of a trapezoid and includes a graph.
```{r}
area_trapezoid(24, 2459, 4, 1)
```

### Area of a Pentagon

This function `area_pentagon(length, apothem, graph)` calculates the area of a $regular$ pentagon, along with, when requested a graph of the pentagon in question. 

The function requires `length`, `apothem`, and `graph` inputs, where `length` is the side length of the pentagon, and `apothem` is the apothem. The final input `graph`, asks the user whether they would like the pentagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length` and `apothem` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_pentagon(length,apothem)`, to do the graphing for it.

This calculates the area of a pentagon with no graph.
```{r}
area_pentagon(4,6,0)
```

This calculates the area of a pentagon and includes a graph.
```{r}
area_pentagon(4,6,1)
```

### Area of a Hexagon

This function `area_hexagon(length, graph)` calculates the area of a $regular$ hexagon, along with, when requested a graph of the hexagon in question. 

The function requires `length`, and `graph` inputs, where `length` is the side length of the regular hexagon. The other input `graph`, asks the user whether they would like the hexagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length`, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_hexagon(x)`, to do the graphing for it.

This calculates the area of a hexagon with no graph.
```{r}
area_hexagon(4,0)
```

This calculates the area of a hexagon and includes a graph.
```{r}
area_hexagon(4,1)
```

### Area of a Octagon

This function `area_octagon(length, graph)` calculates the area of a $regular$ octagon, along with, when requested a graph of the octagon in question. 

The function requires `length`, and `graph` inputs, where `length` is the side length of the regular octagon. The other input `graph`, asks the user whether they would like the octagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_octagon(x)`, to do the graphing for it.

This calculates the area of a octagon with no graph.
```{r}
area_octagon(17,0)
```

This calculates the area of a hexagon and includes a graph.
```{r}
area_octagon(17,1)
```

## Volume Functions
### Volume Cube

The function `volume_cube(length)` calculates the volume of a cube with the provided dimensions. The user must provide the `length` dimension, which is the length of one edge of the cube. 

The inputs for all of these parameters must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_cube(5)
```

### Volume Cylinder

The function `volume_cylinder(base_radius, height)` calculates the volume of a cylinder with the provided dimensions. The user provides the `base_radius` which is the radius of the circular base, and the `height` of the cylinder.

The inputs for all of these parameters must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_cylinder(2, 7)
```

### Volume Tube

The function `volume_tube(outer_radius, inner_radius, height)` calculates the volume of a tube with the given dimensions. The user provides the `outer_radius` which is the radius of the outer circle, the `inner_radius` which is the radius of the inner circle, and the `height` which is the height of the tube. 

The inputs for all of these parameters must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_tube(7, 3, 5)
```

### Volume Ellipsoid

The function `volume_ellipsoid(semi_axe_1, semi_axe_2, semi_axe_3)` calculates the volume of a tube with the given dimensions. The user provides the `semi_axe_1` which is the dimension of the first semi-axe of the ellipsoid, the `semi_axe_2` which is the dimension of the second semi-axe of the ellipsoid, and the `semi_axe_3` is the final semi-axe of the ellipsoid. 

The inputs for all of these parameters must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_ellipsoid(3,5,6)
```

### Volume Sphere

The function `volume_sphere(radius)` calculates the volume of a tube with the given dimensions. The user provides the `radius` which is the radius of the sphere.

The inputs for this parameter must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_sphere(3)
```

### Volume Hemisphere

The function `volume_hemisphere(base_radius)` calculates the volume of a tube with the given dimensions. The user provides the `base_radius` which is the radius of the base circle.

The inputs for this parameter must be numeric and greater than 0, or the function will throw an error.

```{r}
volume_hemisphere(3)
```

### Volume Capsule

### Volume Prism

### Volume Rectangular Solid

### Volume Circular Cone

### Volume Tetrahedron



