---
title: "shapez package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shapez}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette summarizes the various information scattered throughout the R documentation and brings it together in one place. It goes through all of the functions in the package, their specifications, and examples.

### Loading the Package 

```{r setup}
library(shapez)
```

## Area Functions
### Area of a Rectangle

This function `area_square(x, y, graph)` gives the simple area of a rectangle, along with, when requested a graph of the rectangle in question. 

The function requires `x`, `y`, and `graph` inputs, where `x` is the width of the rectangle, and `y` is the height. The final input `graph`, asks the user whether they would like the rectangle to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `x` and `y` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. 

This calculates the area of a rectangle with no graph.
```{r}
area_rectangle(3, 5, 0)
```

This calculates the area of a rectangle and includes a graph.
```{r}
area_rectangle(3, 5, 1)
```

### Area of a Circle

This function `area_circle(x, graph)` gives the simple area of a circle, along with, when requested a graph of the circle in question. 

The function requires `x`, and `graph` inputs, where `x` is the radius of the circle. The other input `graph`, asks the user whether they would like the shape to be graphed. Imputing a 0 will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `x` input, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. 

This calculates the area of a rectangle with no graph.
```{r}
area_circle(3, 0)
```

This calculates the area of a rectangle and includes a graph.
```{r}
area_circle(3, 1)
```

### Area of a Triangle

This function `area_triangle(x, y, graph)` gives the simple area of a triangle, along with, when requested a graph of the triangle in question. 

The function requires `x`, `y`, and `graph` inputs, where `x` is the base of the triangle, and `y` is the height. The final input `graph`, asks the user whether they would like the triangle to be graphed. Imputing a 0 will simply compute the area and not graph the shape; however, the user must know whether the triangle is a right or isosceles triangle to graph it. Inputting a 1 indicates that the triangle is an isosceles and inputting a 2 indicates it is a right triangle, and they will be graphed as such. 

Any negative or string inputs will throw an error for the `x` and `y` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. 

This calculates the area of a triangle with no graph.
```{r}
area_triangle(3, 5, 0)
```

This calculates the area of an isosceles triangle with a graph.
```{r}
area_triangle(3, 5, 1)
```

This calculates the area of an right triangle with a graph.
```{r}
area_triangle(3, 5, 2)
```

### Area of a Trapezoid

### Area of a Pentagon

### Area of a Hexagon

### Area of a Octagon

## Volume Functions


