---
title: "shapez package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shapez}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette summarizes the various information scattered throughout the R documentation and brings it together in one place. It goes through all of the functions in the package, their specifications, and examples.

### Loading the Package 

```{r setup}
library(shapez)
```

## Area Functions
### Area of a Rectangle

This function `area_square(x, y, graph)` gives the simple area of a rectangle, along with, when requested a graph of the rectangle in question. 

The function requires `x`, `y`, and `graph` inputs, where `x` is the width of the rectangle, and `y` is the height. The final input `graph`, asks the user whether they would like the rectangle to be graphed. This may help people to visualize what they are measuring. 

```{r}
area_rectangle(3, 5, 0)
```

```{r}
area_rectangle(3, 5, 1)
```


### Area of a Circle

### Area of a Triangle

### Area of a Trapezoid

### Area of a Pentagon

### Area of a Hexagon

### Area of a Octagon

## Volume Functions


