---
title: "shapez package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shapez}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This vignette summarizes the various information scattered throughout the R documentation and brings it all together in one place. It goes through all of the functions in the package, their specifications, and examples.

### Loading the Package 

```{r setup}
library(shapez)
```

## Area Functions

The area functions allow for calculating the area of, and graphing, common two-dimensional shapes.

### Area of a Rectangle

This function `area_square(width, height, graph)` calculates the area of a rectangle, along with, when requested a graph of the rectangle in question. 

The function requires `width`, `height`, and `graph` inputs, where `width` is the width of the rectangle, and `height` is the height. The final input `graph`, asks the user whether they would like the rectangle to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `width` and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_square(x,y)`, to do the graphing for it. All of the graphing function can be called on their own, but are less user friendly.
```{r}
graph_square(3,5)
```


This calculates the area of a rectangle with no graph.
```{r}
area_rectangle(3, 5, 0)
```

This calculates the area of a rectangle and includes a graph.
```{r}
area_rectangle(3, 5, 1)
```

### Area of a Circle

This function `area_circle(radius, graph)` calculates area of a circle, along with, when requested a graph of the circle in question. 
The function requires `radius`, and `graph` inputs, where `radius` is the radius of the circle. The other input `graph`, asks the user whether they would like the shape to be graphed. Imputing a 0 will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `radius` input, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_circle(x)`, to do the graphing for it.

This calculates the area of a circle with no graph.
```{r}
area_circle(3, 0)
```

This calculates the area of a circle and includes a graph.
```{r}
area_circle(3, 1)
```

### Area of a Triangle

This function `area_triangle(base, height, graph)` calculates the area of a triangle, along with, when requested a graph of the triangle in question. 

The function requires `base`, `height`, and `graph` inputs, where `base` is the base of the triangle, and `height` is the height. The final input `graph`, asks the user whether they would like the triangle to be graphed. Imputing a 0 will simply compute the area and not graph the shape; however, the user must know whether the triangle is a right or isosceles triangle to graph it. Inputting a 1 indicates that the triangle is an isosceles and inputting a 2 indicates it is a right triangle, and they will be graphed as such. 

Any negative or string inputs will throw an error for the `base` and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_triangle(x,y,type)`, to do the graphing for it.

This calculates the area of a triangle with no graph.
```{r}
area_triangle(3, 5, 0)
```

This calculates the area of an isosceles triangle with a graph.
```{r}
area_triangle(3, 5, 1)
```

This calculates the area of an right triangle with a graph.
```{r}
area_triangle(3, 5, 2)
```

### Area of a Trapezoid

This function `area_trapezoid(base_1, base_2, height, graph)` calculates the area of a $regular$ trapezoid along with, when requested, a graph of the trapezoid in question. 

The function requires `base_1`, `base_2`, `height`, and `graph` inputs, where `base_1` is the length of the bottom base, `base_2` is the length of the top base, and `height` being the height of the trapezoid. The final input `graph`, asks the user whether they would like the trapezoid to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape. 

Any negative or string inputs will throw an error for the `base_1`, `base_2`, and `height` inputs, and anything other than a 0 or 1 will throw an error for the graph. This function calls another function `graph_trapezoid(x,y,z)`, to do the graphing for it.

The main purpose of the graph is to help people visualize what area is being measuring. 

This calculates the area of a trapezoid with no graph.
```{r}
area_trapezoid(2, 3, 4, 0)
```

This calculates the area of a trapezoid and includes a graph.
```{r}
area_trapezoid(2, 3, 4, 1)
```

### Area of a Pentagon

This function `area_pentagon(length, apothem, graph)` calculates the area of a $regular$ pentagon, along with, when requested a graph of the pentagon in question. 

The function requires `length`, `apothem`, and `graph` inputs, where `length` is the side length of the pentagon, and `apothem` is the apothem. The final input `graph`, asks the user whether they would like the pentagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length` and `apothem` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_pentagon(length,apothem)`, to do the graphing for it.

This calculates the area of a pentagon with no graph.
```{r}
area_pentagon(4,6,0)
```

This calculates the area of a pentagon and includes a graph.
```{r}
area_pentagon(4,6,1)
```

### Area of a Hexagon

This function `area_hexagon(length, graph)` calculates the area of a $regular$ hexagon, along with, when requested a graph of the hexagon in question. 

The function requires `length`, and `graph` inputs, where `length` is the side length of the regular hexagon. The other input `graph`, asks the user whether they would like the hexagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length`, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_hexagon(x)`, to do the graphing for it.

This calculates the area of a hexagon with no graph.
```{r}
area_hexagon(4,0)
```

This calculates the area of a hexagon and includes a graph.
```{r}
area_hexagon(4,1)
```

### Area of a Octagon

This function `area_octagon(length, graph)` calculates the area of a $regular$ octagon, along with, when requested a graph of the octagon in question. 

The function requires `length`, and `graph` inputs, where `length` is the side length of the regular octagon. The other input `graph`, asks the user whether they would like the octagon to be graphed. If the user inputs a 0, the function will simply compute the area and not graph the shape, but inputting a 1 will graph the shape.

Any negative or string inputs will throw an error for the `length` inputs, and anything other than a 0 or 1 will throw an error for the graph. 

The main purpose of the graph is to help people visualize what area is being measuring. This function calls another function `graph_octagon(x)`, to do the graphing for it.

This calculates the area of a octagon with no graph.
```{r}
area_octagon(17,0)
```

This calculates the area of a hexagon and includes a graph.
```{r}
area_octagon(17,1)
```

### Area Nanogon

This function `area_nonagon(length)` calculates the area of a $regular$ nonagon. It requires the input `lenght`, which is teh length of one side of the regular nonagon. 

Any negative or string inputs will throw an error for the `length` inputs. And this is the only area function without an accompanying graph. 

This calculates the area of a nonagon.
```{r}
area_nonagon(5)
```





## Volume/Surface Area Functions

These functions allow for the calculation of volumes and surface areas of some common three-dimensional shapes.

### Cube

The function `cube(length, return)` calculates the surface area, or volume, or both of a cube with the provided dimensions. The user must provide the `length` dimension, which is the length of one edge of the cube. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for all of these parameters must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
cube(5, "volume")
```

### Capsule

The function `capsule(side_len, radius, return)` calculates the surface area, or volume, or both of a capsule with the provided dimensions. The user provides `side_len` which is a numeric flat side length of the capsule. Additionally, the numeric`radius` argument is required for the radius of hemisphere shaped part of the capsule dimension. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for all of these dimension parameters must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
capsule(2, 7, "surface area")
```


### Sphere

The function `sphere(radius, return = ...)` calculates the surface area, or volume, or both of a sphere with the given dimensions. The user provides the `radius` which is the radius of the sphere. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for this dimension parameter must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
sphere(3, "volume")
```

### Hemisphere

The function `hemisphere(base_radius, return)` calculates the surface area, volume, or both of a hemisphere with the given dimensions. The user provides the `base_radius` which is the radius of the base circle. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for this dimension parameter must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
#volume_hemisphere(3)
```


### Rectangular Prism

The function `rectangular_prism(lenght, width, height, return)` calculates the surface area, or volume, or both of a rectangular prism with the provided dimensions. The user provides the `length`, which is the length of the solid, the `width` which is the width of the prism, and the `height` which is the height dimension of the rectangular prism There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for these dimension parameters must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
rectangular_prism(2, 5, 7, "volume")
```

### Tetrahedron

The function `tetrahedron(length, return)` calculates the surface area, or volume, or both of a tetrahedron with the provided dimension. The user provides the `length`, which is the length of the edge of the tetrahedron. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for this dimension parameter must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
tetrahedron(10)
```


### Square Pyramid

The function `square_pyramid(side_len, height, return)` calculates the surface area, or volume, or both of a square pyramid with the provided dimension. The user must provide `side_len` for the side length of the base. Additionally, they must also privde `height` for the height of the pyramid. There is also a `return` parameter which specifies the desired output result of "volume", "surface area" or "both". The default value is `both`.

The inputs for these dimension parameter must be numeric and greater than 0, or the function will throw an error. Moreover, if a `return` argument is provided, it must be a string of either "volume", "surface area" or "both".

```{r}
square_pyramid(10,12)
```


